\documentclass[12pt]{article}
\usepackage[normalem]{ulem}


\begin{document}
 \pagenumbering{gobble}
\begin{center}
\Huge
Welcome to Zadar!
\end{center}
\uwave{\hspace{15cm}}

\large
\vspace{0.5cm}
\noindent
Here are some basic information that may be helpful during your stay in Zadar.


\vspace{0.5cm}
\noindent
WiFi Information:
\begin{itemize}
\item SSID: ISKONOVAC-6b2100
\item Password: INNBOX3137002395
\end{itemize}



\vspace{0.5cm}

\noindent
\large
Important phone numbers:
\begin{itemize}
\large
\item Ambulance: 194
\item Firefighters: 193
\item Police: 192
\item SOS: 112
\end{itemize}

\vspace{0.5cm}
\noindent
\large
Local Taxies:
\begin{itemize}
\large
\item Uber
\item Bolt
\item Taxi Denis: +385 91 262 262 1
\item Taxi Lulić: +385 23 494 494
\item Taxi Ivana: +385 99 83 27 383
\end{itemize}
\newpage
\noindent
In the immediate vicinity of Zadar, there are four national parks of Croatia:
\begin{itemize}
\large
\item \textbf{NP Krka} - tel. +385 22 201 777, e-mail: info@npk.hr, www.npkrka.hr - located 45 min drive from Zadar
\item \textbf{NP Kornati} - www.kornati.hr - boat tour from Zadar
\item \textbf{NP Plitvice Lakes} - tel. +385 53 751 014, email: info@np-plitvicka-jezera.hr - located about 2 hours drive from Zadar
\item \textbf{NP Paklenica} - tel. +385 23 369 155, email: np-paklenica@paklenica.hr,  located about 30 min drive from Zadar 
\end{itemize}
\noindent
There are also some other natural preserves in the near of Zadar like:
\begin{itemize}
\large
\item \textbf{Zrmanja River} - Rafting, Kayaking and Camping on the Zrmanja river are very popular - www.f-zrmanja.com
\item \textbf{Velebit Nature Park} - Most popular hiking trails in Croatia - email: velebit@pp-velebit.hr, www.velebit.hr
\end{itemize}

\vspace{1cm}
\noindent
\textbf{ZADAR AIRPORT}


\noindent
Tel. +385 23 205 800, e-mail:info@zadar-airport.hr

\noindent
Lost \& Found - tel. +385 23 205 904

\noindent
Buses to the airport leave from the central bus station in Zadar. Buses are clean, comfortable and efficient. The bus ticket cost around 30 HRK (4 EUR). There are no luggage fees.

\newpage


\end{document}